Stimulated Accretion from Circumgalactic Media Interactions

### 2024-02-12 paper/ms.tex
Update abstract for interacting CGM direction

\shorttitle{Hydrodynamics of the GSE Merger}
\shortauthors{Beane et al.}

@@

\title{Diluting the Merger Scenario for the Alpha Bimodality}

@@

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  The merger at $z\sim2$ between the proto-Milky Way and the
  Gaia-Sausage-Enceladus (GSE) satellite shaped the present day stellar halo and
  possibly led to the formation of the alpha-abundance bimodality seen in the
  disk today. Cosmological zoom simulations of GSE-like mergers have shown that
  the alpha bimodality can be explained by a dilution of the Milky Way's metal
  content by GSE. However, radial migration processes alone can also produce
  alpha bimodalities without the need for a fresh, metal-poor gas supply. We
  present simulations of a controlled GSE-like merger. Our simulations include
  gaseous disks, circumgalactic media, and a modern model for the interstellar
  medium, star formation, and stellar feedback. We argue that because GSE's
  orbit was mildly retrograde but mostly polar on second pericentric passage,
  the gas from GSE was able to penetrate the inner disk of the Milky Way. It
  therefore dilutes the inner Galaxy more strongly than the outer Galaxy. Models
  which explain the alpha bimodality from the GSE merger require the outer disk
  to be more diluted than the inner disk. It would seem that our results stand
  in direct opposition with the picture that the alpha bimodality resulted from
  the GSE merger.
\end{abstract}

@@

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

>>>>

\shorttitle{The CGM of Merging Galaxies}
\shortauthors{Beane et al.}

@@

\title{Stimulated Accretion from Circumgalactic Media Interactions}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  It is now well-established that galaxies host extended gaseous haloes dubbed
  the circumgalactic medium (CGM) which play a critical role in receiving and
  providing gas from and to the disk. Typically metal-poor, the CGM is a major
  actor in the nuclear abundance evolution of galaxies. While aspects of
  isolated CGM, such as its rotation and multiphase nature, have been studied,
  the interaction between the CGM of two merging galaxies is less well
  understood. In this work, we present hydrodynamic simulations of a controlled
  galaxy merger, roughly resembling a merger the Milky Way experienced early in
  its history. Unsurprisingly, the CGM of the satellite galaxy is stripped early
  in the merger -- mostly during its first pericentric passage (check). This has
  the effect of stimulating the accretion of gas from the host's CGM onto its
  disk. This occurs due to two effects: (1) Cold gas from the satellite's CGM
  mixes with gas in the host's CGM and cools it to a regime where cooling is
  more efficient, thus reducing the gas' thermal pressure support. (2) The
  satellite deepens the potential well of the host galaxy, reducing its
  free-fall time. These effects combine to enhance the accretion of gas onto the
  host's disk. In our setup (for which there is significant uncertainty), the
  bulk amount of gas accreted on the disk can increase by a factor of $\sim2$
  (\textcolor{red}{checl}).
\end{abstract}

@@
